Summary of ConvSmall

### 2024-04-03 Reports/Summary of tests on MNIST ConvSmall.tex
fix typo
fix typos

	Average time of open 100, 200, 250 are 467.0s, 411.8s, 501.5s (including previous layers).

@@

	\end{enumerate}

>>>>

	Average time of open 100, 200, 250 are 411.8s, 467.0s,  501.5s (including previous layers).

@@

	\end{enumerate}
	\vspace*{2ex}

	One question is that, even I open all unstable nodes in layer 5, the bounds of layer 5 will still heavily influence the accuracy of layer 7. Why?
